RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
corrected capitalization

<!-- have we already said all this above?-->  <!-- no, seems appropriate to repeat here, -scott --> The ability to read in
phylogenetic trees in the `nexml` format opens up a wide and rapidly
growing array of resources to the R user.  For instance, a user can access
all the phylogenies available in TreeBASE through the `nexml` format.
`RNeXML` can read directly from a URL:

>>>>

<!-- have we already said all this above?-->  <!-- no, seems appropriate to repeat here, -scott --> The ability to read in
phylogenetic trees in the NeXML format opens up a wide and rapidly
growing array of resources to the R user.  For instance, a user can access
all the phylogenies available in TreeBASE through the `nexml` format.
`RNeXML` can read directly from a URL:
